Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-04 Submission.Rmd
updating the results section

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand. We would expect to see minimal correlations if job characteristics *were* uniquely categorized. Here, we do expected to see more than minimal correlations. First, the mean correlation within resource categories was __________, _________ within challenge categories, and __________ within hindrance categories. We would expect these to be the highest. The mean resource to challenge correlation was __________. The mean resource to hindrance correlation was __________. Finally, the mean challenge to hindrance correlation was ____________. These were expected to be moderate in size, but smaller than within the same category. In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a *resource* being also perceived as a *challenge*. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

r <- corx::corx(data_new, x =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo",  "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"), y =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo", "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"),            
                triangle = "upper",
  #              stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

>>>>

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand. We would expect to see minimal correlations if job characteristics *were* uniquely categorized. Here, we do expected to see more than minimal correlations. First, the mean correlation within resource categories was .43 (*SD* = .13, range from .15 to .64), and challenge categories were similar (ranging from .12 to .70, *M* = .43, *SD* =.16). Hindrance categories had less differentiation across categories ranging from .33 to .86, *M* = .62, *SD* = .17. When people perceived hindrances, these seemed to be shared across different types of job activities, whereas challenges challenges and resources exhibited more differentiation.  We would expect these to be the highest.

The mean resource to challenge correlations within the same dimension ranged from .62 to .66, *M* = .64, *SD* = .02). The correlations between resources and challenges across dimensions ranged from .08 to .50, *M* = .32, *SD* = .12. The mean resource to hindrance correlations within the same dimension ranged from -.16 to -.30, *M* = -.24, *SD* = .05). The correlations between resources and hindrances across dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08. The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27, *M* = -.21, *SD* = .08). The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, *M* = -.11, *SD* = .09.  Correlations were larger when what was being rated was the same type of characteristic. In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a *resource* being also perceived as a *challenge*. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

r <- corx::corx(data_new, x =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo",  "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"), y =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo", "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"),            
                triangle = "lower",
 #               stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

### 2023-03-04 Submission.tex
updating the results section

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand. We would expect to see minimal correlations if job characteristics \emph{were} uniquely categorized. Here, we do expected to see more than minimal correlations. First, the mean correlation within resource categories was \_\_\_\_\_\_\_\_\_\_, \_\_\_\_\_\_\_\_\_ within challenge categories, and \_\_\_\_\_\_\_\_\_\_ within hindrance categories. We would expect these to be the highest. The mean resource to challenge correlation was \_\_\_\_\_\_\_\_\_\_. The mean resource to hindrance correlation was \_\_\_\_\_\_\_\_\_\_. Finally, the mean challenge to hindrance correlation was \_\_\_\_\_\_\_\_\_\_\_\_. These were expected to be moderate in size, but smaller than within the same category. In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

1. onet.resource.ii & - & .61* & .46* & .49* & .46* & .19* & .43* & .62* & .47* & .34* & .34* & .32* & .12* & .27* & -.26* & -.23* & -.21* & -.22* & -.22* & -.04 & 3.98 & 0.80\\
2. onet.resource.mp &  & - & .50* & .64* & .55* & .15* & .46* & .49* & .63* & .39* & .48* & .40* & .08 & .31* & -.26* & -.30* & -.25* & -.27* & -.24* & -.08* & 4.19 & 0.60\\
3. onet.resource.wo &  &  & - & .45* & .37* & .32* & .41* & .37* & .42* & .64* & .33* & .26* & .21* & .28* & -.17* & -.17* & -.22* & -.14* & -.15* & -.09* & 3.79 & 0.84\\
4. onet.resource.io &  &  &  & - & .60* & .18* & .45* & .41* & .50* & .34* & .65* & .48* & .13* & .38* & -.24* & -.22* & -.22* & -.29* & -.24* & -.11* & 4.10 & 0.60\\
5. onet.resource.ir &  &  &  &  & - & .37* & .48* & .33* & .41* & .30* & .48* & .63* & .26* & .40* & -.18* & -.15* & -.06 & -.18* & -.25* & -.10* & 3.80 & 0.61\\
6. onet.resource.pc &  &  &  &  &  & - & .37* & .08 & .09* & .29* & .13* & .23* & .66* & .27* & -.02 & .05 & -.02 & -.01 & -.06 & -.16* & 2.99 & 0.77\\
7. onet.resource.sc &  &  &  &  &  &  & - & .33* & .38* & .38* & .40* & .39* & .29* & .62* & -.08 & -.07 & -.12* & -.10* & -.11* & -.13* & 3.65 & 0.61\\
8. onet.challenge.ii &  &  &  &  &  &  &  & - & .65* & .45* & .50* & .46* & .14* & .36* & -.27* & -.22* & -.14* & -.21* & -.19* & -.03 & 3.98 & 0.80\\
9. onet.challenge.mp &  &  &  &  &  &  &  &  & - & .49* & .68* & .60* & .12* & .41* & -.26* & -.27* & -.21* & -.25* & -.21* & -.04 & 4.20 & 0.64\\
10. onet.challenge.wo &  &  &  &  &  &  &  &  &  & - & .43* & .39* & .33* & .38* & -.10* & -.10* & -.23* & -.10* & -.08* & -.06 & 3.65 & 0.88\\
11. onet.challenge.io &  &  &  &  &  &  &  &  &  &  & - & .70* & .20* & .51* & -.19* & -.18* & -.15* & -.27* & -.20* & -.08* & 4.07 & 0.64\\
12. onet.challenge.ir &  &  &  &  &  &  &  &  &  &  &  & - & .31* & .45* & -.16* & -.15* & -.09* & -.19* & -.23* & -.10* & 3.85 & 0.63\\
13. onet.challenge.pc &  &  &  &  &  &  &  &  &  &  &  &  & - & .40* & .06 & .12* & .05 & .07 & .04 & -.04 & 2.85 & 0.79\\
14. onet.challenge.sc &  &  &  &  &  &  &  &  &  &  &  &  &  & - & -.10* & -.06 & -.10* & -.10* & -.12* & -.13* & 3.66 & 0.59\\
15. onet.hindrance.ii &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .86* & .66* & .79* & .79* & .38* & 2.15 & 1.01\\
16. onet.hindrance.mp &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .69* & .86* & .80* & .33* & 2.10 & 1.05\\
17. onet.hindrance.wo &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .69* & .61* & .47* & 2.31 & 1.02\\
18. onet.hindrance.io &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .82* & .35* & 2.23 & 1.03\\
19. onet.hindrance.ir &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .47* & 2.35 & 0.89\\
20. onet.hindrance.pc &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & 2.66 & 0.83\\
21. onet.hindrance.sc &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.64 & 0.80\\

>>>>

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand. We would expect to see minimal correlations if job characteristics \emph{were} uniquely categorized. Here, we do expected to see more than minimal correlations. First, the mean correlation within resource categories was .43 (\emph{SD} = .13, range from .15 to .64), and challenge categories were similar (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16). Hindrance categories had less differentiation across categories ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17. When people perceived hindrances, these seemed to be shared across different types of job activities, whereas challenges challenges and resources exhibited more differentiation. We would expect these to be the highest.

The mean resource to challenge correlation was \_\_\_\_\_\_\_\_\_\_. The mean resource to hindrance correlation was \_\_\_\_\_\_\_\_\_\_. Finally, the mean challenge to hindrance correlation was \_\_\_\_\_\_\_\_\_\_\_\_. These were expected to be moderate in size, but smaller than within the same category. In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
2. onet.resource.mp & .61* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
3. onet.resource.wo & .46* & .50* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
4. onet.resource.io & .49* & .64* & .45* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
5. onet.resource.ir & .46* & .55* & .37* & .60* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
6. onet.resource.pc & .19* & .15* & .32* & .18* & .37* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
7. onet.resource.sc & .43* & .46* & .41* & .45* & .48* & .37* & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
8. onet.challenge.ii & .62* & .49* & .37* & .41* & .33* & .08 & .33* & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
9. onet.challenge.mp & .47* & .63* & .42* & .50* & .41* & .09* & .38* & .65* & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
10. onet.challenge.wo & .34* & .39* & .64* & .34* & .30* & .29* & .38* & .45* & .49* & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
11. onet.challenge.io & .34* & .48* & .33* & .65* & .48* & .13* & .40* & .50* & .68* & .43* & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
12. onet.challenge.ir & .32* & .40* & .26* & .48* & .63* & .23* & .39* & .46* & .60* & .39* & .70* & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
13. onet.challenge.pc & .12* & .08 & .21* & .13* & .26* & .66* & .29* & .14* & .12* & .33* & .20* & .31* & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
14. onet.challenge.sc & .27* & .31* & .28* & .38* & .40* & .27* & .62* & .36* & .41* & .38* & .51* & .45* & .40* & - &  &  &  &  &  &  & 3.66 & 0.59\\
15. onet.hindrance.ii & -.26* & -.26* & -.17* & -.24* & -.18* & -.02 & -.08 & -.27* & -.26* & -.10* & -.19* & -.16* & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
16. onet.hindrance.mp & -.23* & -.30* & -.17* & -.22* & -.15* & .05 & -.07 & -.22* & -.27* & -.10* & -.18* & -.15* & .12* & -.06 & .86* & - &  &  &  &  & 2.10 & 1.05\\
17. onet.hindrance.wo & -.21* & -.25* & -.22* & -.22* & -.06 & -.02 & -.12* & -.14* & -.21* & -.23* & -.15* & -.09* & .05 & -.10* & .66* & .69* & - &  &  &  & 2.31 & 1.02\\
18. onet.hindrance.io & -.22* & -.27* & -.14* & -.29* & -.18* & -.01 & -.10* & -.21* & -.25* & -.10* & -.27* & -.19* & .07 & -.10* & .79* & .86* & .69* & - &  &  & 2.23 & 1.03\\
19. onet.hindrance.ir & -.22* & -.24* & -.15* & -.24* & -.25* & -.06 & -.11* & -.19* & -.21* & -.08* & -.20* & -.23* & .04 & -.12* & .79* & .80* & .61* & .82* & - &  & 2.35 & 0.89\\
20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11* & -.10* & -.16* & -.13* & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13* & .38* & .33* & .47* & .35* & .47* & - & 2.66 & 0.83\\
21. onet.hindrance.sc & -.13* & -.15* & -.13* & -.19* & -.13* & -.09* & -.23* & -.12* & -.10* & -.05 & -.16* & -.12* & -.01 & -.17* & .62* & .62* & .56* & .64* & .66* & .45* & 2.64 & 0.80\\
